Modelling Prehistorical Iconographic Compositions. The \proglang{R} package \pkg{decorr}

### 2020-11-06 article_rvTH15_6.Rnw
neww changes

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Thomas Huet\\UMR 5140}
%   \And Second Author\\Plus Affiliation}
\Plainauthor{Thomas Huet}

@@

\begin{figure}[H] 
\centering
\includegraphics[scale=0.15]{gis_1}
\caption{\label{fig:gis1} GIS interface. The GUs \code{casque} (helmet) and \code{sexe\_masculin} (male sex) are two attributes of the GU \code{personnage} (character).}
\end{figure}

>>>>

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Thomas Huet\\UMR 5140 \And Craig Alexander \And Jose Pozo}
%   \And Second Author\\Plus Affiliation}
\Plainauthor{Thomas Huet, Craig Alexander, Jose Pozo}

@@

\begin{figure}[H] 
\centering
\includegraphics[scale=0.15]{gis_1}
\caption{\label{fig:gis1} GIS interface. The GUs \code{casque} (helmet) and \code{sexe\_masculin} (male sex) are two nodes attributes of the GU \code{personnage} (character).}
\end{figure}
